\section{Introduction}
\paragraph{}
The profession I am interested in is being a Systems Administrator, otherwise
known as a SysAdmin. Systems Administrators:


\begin{itemize}
	\item{Deploy, Maintain, \& Troubleshoot:}
		\begin{itemize}
			\item{Computers}
			\item{Networks}
			\item{Software}
			\item{More}
		\end{itemize}
\end{itemize}

At least that's what SysAdmins do in a very boiled down, basic sense.
\par
\section{Profession}

\subsection{Education}
\paragraph{}

A SysAdmin typically has a layered education. This starts with the basics and
builds upon then keeps building on the foundation of their previous education.
Some degrees and certifications a SysAdmin might have are:

\begin{itemize}
	\item{A+ Certification}
		\begin{itemize}
			\item{Confirmation of a basic understanding of hardware and software.\cite{comptia}}
		\end{itemize}
	\item{CIT Degree}
		\begin{itemize}
			\item{The practical application of computers in a commercial environment.\cite{davidhandlos}}
		\end{itemize}
	\item{CIS Degree}
		\begin{itemize}
			\item{Project management.\cite{davidhandlos}}
			\item{Managerial Communications.}
			\item{Practical use of computers in a commercial environment.\cite{davidhandlos}}
		\end{itemize}
	\item{Computer Science Degree}
		\begin{itemize}
			\item{An understanding of a wide range of programming languages.\cite{topuniversities}}
			\item{Understanding Computer software, tools, packages, and design.\cite{topuniversities}}
			\item{Understanding a range of computer systems.\cite{topuniversities}}
		\end{itemize}
\end{itemize}

Education for a SysAdmin can be gathered through a variety of sources, such as
college, online courses, and vocation schools.
\par

\subsection{Income}
\paragraph{}
the income of a SysAdmin can widely vary, though from what I've gathered, the
income of a system seems to be between: \$51,000K at the lowest, \$65,273 at
average, and \$93,000 at the highest\cite{glassdoor2016}, according to
\href{https://glassdoor.com}{glassdoor.com}.
\par

\section{The progression of a SysAdmin}

\subsection{Education}
\paragraph{}
Like any profession, the first step is to get educated. This might start out as
formal or informal education (i.e.\ self-learning, or learning in a structured
environment). Though it will eventually progress to something like a technical
school, otherwise known as a vocational school where you can earn some basic
form of certification. After this college is most likely next to get a degree
of some sort, to further solidify your knowledge in the field.
\par

\subsection{Career Experience}
\paragraph{}
Either during or After formal education one can aquire career experience.
Having Experience in your field (Whether it be formal employment, or volunteer
work) Will certainly help you along your way to becoming a SysAdmin and open
oppurtunities for future employment.
\par

\subsection{Job Acquired?}
\paragraph{}
While it is very unlikely to get a SysAdmin position right off the bat, there is
always the possibility of it happening.
\par

\printbibliography{}
